Article title

### 2019-07-08 NAR_DRAFT.tex
make tiny for now

We develop a method, following \citet{Efron2008}, for controlling the false positive rate.
Every site with sufficient coverage and at least 1 alternate read falls into one of two classes, they are either *null* (non-variant with $\nu = 0$) or *nonnull* (variant with $\nu = \hat{f}$) with prior probabilities $p_0$ and $p_1 = 1-p_0$,

@@

The local, or site-specific, true positive probability $p_1$ can be estimated as the fraction of all sequenced sites that are expected to be positive.
In a neutrally evolving tumor, the number of cells is growing exponentially, and the count of variants with an allele frequency greater than a given allele frequency $f$ is \cite{Bozic2016,Williams2016a}.
$$
N(f) = \frac{N\mu}{f},
$$
Where $N$ is the total number of sites sequenced and $\mu$ is the per-site mutation probability.
The estimated fraction of all of the sites in the genome that will have a mutation with frequency $f$ is
$$
\hat{p}_1 = \frac{\int_{f_{-}}^{f_{+}} N(f)}{N} = \frac{\mu}{f - .1f} -  \frac{\mu}{f + .1f}
$$
and the estimated null probability $\hat{p}_0 = 1 - \hat{p}_1$.
citet{Williams2016a} provides a full derivation for this, we are essentially computing the integral here of $N(f)$ in a small area around $f$.

@@

\begin{verbatim}
java -Xmx24g -jar $MUTECT_JAR --analysis_type MuTect --reference_sequence $ref_path \
        --dbsnp $db_snp \
        --enable_extended_output \
        --fraction_contamination 0.00 \
        --tumor_f_pretest 0.00 \
        --initial_tumor_lod -10.00 \
        --required_maximum_alt_allele_mapping_quality_score 1 \
        --input_file:normal $tmp_normal \
        --input_file:tumor $tmp_tumor \
        --out $out_path/$chr.txt \
        --coverage_file $out_path/$chr.cov
\end{verbatim}

Variants identified by MuTect are labelled as to whether they pass all MuTect filters, pass all filters *other* than the evidence threshold \textrm{tlod\_f\_star}, or fail to pass any filter other than \textrm{tlod\_f\_star}. Variants that pass all filters or fail only \textrm{tlod\_f\_star} are then passed to {method} for prior estimation and rescoring.

>>>>

We develop a method, following \citet{Efron2008}, for controlling the false positive rate.
Every site with sufficient coverage and at least 1 alternate read falls into one of two classes, they are either \textit{null} (non-variant with $\nu = 0$) or \textit{nonnull} (variant with $\nu = \hat{f}$) with prior probabilities $p_0$ and $p_1 = 1-p_0$,

@@

The local, or site-specific, true positive probability $p_1$ can be estimated as the fraction of all sequenced sites that are expected to be positive.
In a neutrally evolving tumor, the number of cells is growing exponentially, and the count of variants with an allele frequency greater than a given allele frequency $f$ is \cite{Bozic2016,Williams2016a}.
$$
N(f) = \frac{N\mu}{f},
$$
Where $N$ is the total number of sites sequenced and $\mu$ is the per-site mutation probability.
The estimated fraction of all of the sites in the genome that will have a mutation with frequency $f$ is
$$
\hat{p}_1 = \frac{\int_{f_{-}}^{f_{+}} N(f)}{N} = \frac{\mu}{f - .1f} -  \frac{\mu}{f + .1f}
$$
and the estimated null probability $\hat{p}_0 = 1 - \hat{p}_1$.
\citet{Williams2016a} provides a full derivation for this, we are essentially computing the integral here of $N(f)$ in a small area around $f$.

\subsubsection{Tumor simulations.}

@@

\begin{tiny}
\begin{verbatim}

  java -Xmx24g -jar $MUTECT_JAR --analysis_type MuTect --reference_sequence $ref_path \
        --dbsnp $db_snp \
        --enable_extended_output \
        --fraction_contamination 0.00 \
        --tumor_f_pretest 0.00 \
        --initial_tumor_lod -10.00 \
        --required_maximum_alt_allele_mapping_quality_score 1 \
        --input_file:normal $tmp_normal \
        --input_file:tumor $tmp_tumor \
        --out $out_path/$chr.txt \
        --coverage_file $out_path/$chr.cov

\end{verbatim}
\end{tiny}
Variants identified by MuTect are labelled as to whether they pass all MuTect filters, pass all filters *other* than the evidence threshold \textrm{tlod\_f\_star}, or fail to pass any filter other than \textrm{tlod\_f\_star}. Variants that pass all filters or fail only \textrm{tlod\_f\_star} are then passed to {method} for prior estimation and rescoring.
